\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-30 paper.qmd
Added python packages
Added Figure 9 title

```{r}
#| echo: false
#| fig-cap: "Various plots to help assess best hexagon bin parameters, thresholds to remove low density bins and large edges. Both (b) and (c) show MSE, against number of bins along the x-axis and standardised count. A good benchmark value for these parameters is when the MSE drops and then flattens out. Plot (a) shows the distribution of stadardised counts of hexagons. Plot (d) shows the distribution of $2\\text{-}D$ Euclidean distances between bin centroids, with a good benchmark value for removing large edges would being the distance that shows the first large decrease."
#| label: fig-param-two-curvy
#| out-width: 100%
#| fig-width: 12
#| fig-height: 10
#| fig-pos: H

@@

These `R` packages were used for the work: `tidyverse` (@hadley2019), `png` (@simon2022), `Rtsne` (@jesse2015), `umap` (@tomasz2023), `ggplot2` (@hadley2016), `patchwork` (@thomas2024), `colorspace` (@achim2020), `langevitour` (@harisson2024), `conflicted` (@hadley2023), `reticulate` (@kevin2024), `kableExtra` (@hao2024). These `python` packages were used for the work:. The article was created with `R` packages `rticles` (@jjallaire2024), `knitr` (@yihui2014), and `rmarkdown` (@yihui2020). The project's GitHub repository ([https://github.com/JayaniLakshika/paper-nldr-vis-algorithm](https://github.com/JayaniLakshika/paper-nldr-vis-algorithm)) contains all materials required to reproduce this article.

>>>>

```{r}
#| echo: false
#| fig-cap: "Various plots to help assess best hexagon bin parameters and thresholds to remove low-density bins. Both (a) and (c) show MSE, against binwidth ($a_1$) and threshold. A good benchmark value for these parameters is when the MSE drops and then flattens out. Three binwidth choices were made: $0.05$, $0.09$, and $0.12$ to investigate. As the binwidth increases, the proportion of non-empty bins also increases. There are two peaks at binwidths $0.09$ and $0.12$. The proportion of densities, calculated as a density with the smallest possible binwidth, decreases and levels off. Binwidths $0.09$ and $0.12$ are favorable choices. Based on the MSE, $0.09$ was chosen as the initial best binwidth for further analysis. There is no need to remove the low-density hexagons because as shown in (b), there is no considerable drop in MSE."
#| label: fig-param-two-curvy
#| out-width: 100%
#| fig-width: 12
#| fig-height: 10
#| fig-pos: H

@@

These `R` packages were used for the work: `tidyverse` (@hadley2019), `png` (@simon2022), `Rtsne` (@jesse2015), `umap` (@tomasz2023), `ggplot2` (@hadley2016), `patchwork` (@thomas2024), `colorspace` (@achim2020), `langevitour` (@harisson2024), `conflicted` (@hadley2023), `reticulate` (@kevin2024), `kableExtra` (@hao2024). These `python` packages were used for the work: `trimap` (@amid2022) and `pacmap` (@yingfan2021). The article was created with `R` packages `rticles` (@jjallaire2024), `knitr` (@yihui2014), and `rmarkdown` (@yihui2020). The project's GitHub repository ([https://github.com/JayaniLakshika/paper-nldr-vis-algorithm](https://github.com/JayaniLakshika/paper-nldr-vis-algorithm)) contains all materials required to reproduce this article.

### 2024-09-30 paper.tex
Added Figure 9 title

\caption{\label{fig-param-two-curvy}Various plots to help assess best
hexagon bin parameters, thresholds to remove low density bins and large
edges. Both (b) and (c) show MSE, against number of bins along the
x-axis and standardised count. A good benchmark value for these
parameters is when the MSE drops and then flattens out. Plot (a) shows
the distribution of stadardised counts of hexagons. Plot (d) shows the
distribution of \(2\text{-}D\) Euclidean distances between bin
centroids, with a good benchmark value for removing large edges would
being the distance that shows the first large decrease.}

>>>>

\caption{\label{fig-param-two-curvy}Various plots to help assess best
hexagon bin parameters and thresholds to remove low-density bins. Both
(a) and (c) show MSE, against binwidth (\(a_1\)) and threshold. A good
benchmark value for these parameters is when the MSE drops and then
flattens out. Three binwidth choices were made: \(0.05\), \(0.09\), and
\(0.12\) to investigate. As the binwidth increases, the proportion of
non-empty bins also increases. There are two peaks at binwidths \(0.09\)
and \(0.12\). The proportion of densities, calculated as a density with
the smallest possible binwidth, decreases and levels off. Binwidths
\(0.09\) and \(0.12\) are favorable choices. Based on the MSE, \(0.09\)
was chosen as the initial best binwidth for further analysis. There is
no need to remove the low-density hexagons because as shown in (b),
there is no considerable drop in MSE.}
